Untitled CAV Paper

### 2016-01-20 paper.tex
Added some game tree diagrams and explanation

\documentclass{llncs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\pagestyle{headings}

@@

\subsection{Solving Bounded Runs}

An abstract game tree can be checked for a winning run by a SAT solver.  The
tree must be encoded into CNF by making copies of the transition relation for
each game step in tree. The formula must also check whether the error state has
been reached in no branch/in all branches for the controller and environment
respectively. The functions that produce these formulas are shown in Algorithm
\ref{alg:treeFormula}.

@@

When we produce a formula using $\textsc{treeFormula}$ the SAT solver is
playing on behalf on the controller. Any unfixed labels, controllable or
uncontrollable, in the tree will be existentially quantified. This means that
if there exists a way for the game to be solved when both players cooperate the
SAT solver will find it.

@@

>>>>

\documentclass{llncs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{tikz}
\usetikzlibrary{trees}

\pagestyle{headings}

@@

An abstract game tree can be checked for the existence of a winning run by a
SAT solver.  The tree must be encoded into CNF by making copies of the
transition relation for each game step in tree. The formula must also check
whether the error state has been reached in no branch/in all branches for the
controller and environment respectively. The functions that produce these
formulas are shown in Algorithm \ref{alg:treeFormula}.

@@

When we produce a formula using $\textsc{treeFormula}$ the SAT solver is
playing on behalf on the controller. Any unfixed labels in the tree,
controllable or uncontrollable, will be existentially quantified.  This means
that if there exists a way for the game to be solved when both players
cooperate the SAT solver will find it. If no winning run exists in an abstract
game even when the players are cooperating then there is definitely no winning
run when the opponent is playing adversarily.

@@

By checking for the existence of a winning run for the environment in an
abstract game tree constructed from a partial controller strategy we are
checking if the partial strategy is winning. If no spoiling run can be found
then the partial strategy must always win. If a spoiling run is found then we
then we have a counterexample that proves that the controller strategy is not
winning. This forms the basis of a counterexample guided abstraction refinement
framework that operates on candidate strategies.

Synthesis begins with an empty game as seen in Figure \ref{fig:emptytree}.
Initially we are playing on behalf of the environment because it chooses the
first move in each step. The empty game is passed to the SAT solver, which
searches for a candidate environment strategy.  If a candidate is found (Figure
\ref{fig:candidate}) then it is checked for a spoiling strategy by solving for
the controller. If no spoiling strategy exists, that means our candidate is a
winning strategy and the algorithm terminates.  Otherwise we find a
counterexample (Figure \ref{fig:cex}), which is used to refine the empty game
tree to include the first move from the controller's spoiling strategy (Figure
\ref{fig:refined}.  The algorithm continues by finding a new candidate for the
environment (Figure \ref{fig:candidate2}), and a new counterexample to refine
the game abstraction once again (Figure \ref{fig:refined2}).

\tikzset{every node/.style={solid}}
\tikzstyle{fixed}=[solid]
\tikzstyle{unfixed}=[dash pattern = on 2pt off 2pt]
\begin{figure}
    \centering
    \begin{subfigure}{.3\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] (root){}
                child {node [circle,draw] {} edge from parent[unfixed]
                    child {node [circle,draw] {} edge from parent[unfixed]}
                };
        \end{tikzpicture}
        \caption{An empty AGT}
        \label{fig:emptytree}
    \end{subfigure}%
    \begin{subfigure}{.35\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] (root) {}
                child {node [circle,draw] {}
                    child {node [circle,draw] {} edge from parent[unfixed]}
                    edge from parent [fixed] node [left] {$u_1$}
                };
        \end{tikzpicture}
        \caption{Environment candidate}
        \label{fig:candidate}
    \end{subfigure}%
    \begin{subfigure}{.4\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] (root){}
                child {node [circle,draw] {} edge from parent[unfixed]
                    child {node [circle,draw] {} edge from parent[fixed] node [left] {$c_1$}}
                    edge from parent [fixed] node [left] {$u_1$}
                };
        \end{tikzpicture}
        \caption{Counterexample}
        \label{fig:cex}
    \end{subfigure}

    \begin{subfigure}{.3\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] (root){}
                child {node [circle,draw] {} edge from parent[unfixed]
                    child {node [circle,draw] {} edge from parent[fixed] node [left] {$c_1$}}
                };
        \end{tikzpicture}
        \caption{Refined AGT}
        \label{fig:refined}
    \end{subfigure}%
    \begin{subfigure}{.35\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] (root) {}
                child {node [circle,draw] {}
                    child {node [circle,draw] {} edge from parent[unfixed]}
                    edge from parent [fixed] node [left] {$u_2$}
                };
        \end{tikzpicture}
        \caption{New candidate}
        \label{fig:candidate2}
    \end{subfigure}%
    \begin{subfigure}{.4\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] (root){}
                child {node [circle,draw] {} edge from parent[unfixed]
                    child {node [circle,draw] {} edge from parent[fixed] node [left] {$c_1$}}
                    child {node [circle,draw] {} edge from parent[fixed] node [right] {$c_2$}}
                };
        \end{tikzpicture}
        \caption{Refined AGT}
        \label{fig:refined2}
    \end{subfigure}
    \caption{Abstract game trees}
\end{figure}
